Verifying Demonstrations

### 2018-05-31 paper/intro.tex
Comment's on Seb's comment in contribution

Our second contribution is an adaptation of the Schnorr's protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr's protocol in the \ac{ZKPK} used in anonymous credentials. 
%Seb: I have put the following sentence because due to the amount of current work recently in distance-bounding, I believe that our sentence should be made more reasonable 
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.

\emph{Outline.} 
The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{SystemModel}).  
Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). 
Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{BuildingBlocks}). 
\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}) as well as a discussion of the performance and implementation issues (\cref{PerformanceAnalysis}). 
Finally, we conclude with a discussion and futures works in \cref{Conclusion}.

>>>>

Our second contribution is an adaptation of the Schnorr's protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr's protocol in the 
\ac{ZKPK} used in anonymous credentials.
\seb{I have put the following sentence because due to the amount of current 
  work recently in distance-bounding, I believe that our sentence should be 
  made more reasonable:
  \enquote{and thus we are, to the best of our knowledge, the first to provide 
    \ac{DB} anonymous credentials.}}
\daniel{I quickly looked through the papers from 2015--2018, none seem to do 
  this, they are more about authenticating identities (possibly anonymously), 
  but not fully fledged anonymous credentials --- where we can prove \eg that 
  Alice is indeed older than 18 without revealing her age and that it is not a 
  relay (due to \ac{DB}).}

\emph{Outline.} 
The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{SystemModel}).  
Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). 
Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{BuildingBlocks}). 
\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}) as well as a discussion of the performance and implementation issues (\cref{PerformanceAnalysis}). 
Finally, we conclude with a discussion and future works in \cref{Conclusion}.
